\section{Results}
\label{sec:results}

We present results from three parameter sweeps, each comparing greedy and MCF routing across all three topologies. All sweeps use default parameters ($F_\text{init} = 0.95$, $p_0 = 1.0$, $L_\text{att} = 22$~km, $q_\text{swap} = 1.0$, 500 time steps, seed 42) unless the swept parameter says otherwise.

\paragraph{Cutoff sweep (Fig.~\ref{fig:cutoff}).} We vary $T_\text{cut} \in \{1, 3, 5, 10, 20, 50\}$ with $F_\text{min} = 0.80$. For the scaled US topologies (NSFNET and Abilene), MCF achieves roughly $1.0$ pair/step and remains flat across all cutoff values, while greedy ranges from $0.1$--$0.47$. SURFnet (unscaled) stays below $0.08$ for both algorithms. NSFNET greedy decreases from $\sim$0.39 at $T_\text{cut} = 1$ to $\sim$0.13 at $T_\text{cut} = 50$.

\paragraph{Fidelity threshold sweep (Fig.~\ref{fig:fmin}).} We vary $F_\text{min} \in \{0.50, 0.60, 0.70, 0.80, 0.90\}$ with $T_\text{cut} = 10$. NSFNET and Abilene sustain $\sim$1.25--1.3 pairs/step for both algorithms up to $F_\text{min} = 0.70$. At $F_\text{min} = 0.80$ there is a sharp drop, and by $F_\text{min} = 0.90$ rates fall near zero for all topologies. MCF consistently delivers at higher rates than greedy, with the gap widening at $F_\text{min} = 0.80$--$0.90$. SURFnet rates are $\sim$0.15 or below across the entire sweep.

\paragraph{Per-pair comparison (Fig.~\ref{fig:perpair}).} With default parameters ($T_\text{cut} = 10$, $F_\text{min} = 0.80$), we show delivery rate and average fidelity broken down by user pair. Pairs with 5 or more hops (WA--DC, CA1--NY, SEA--NYC, DEL--ENS) receive zero or near-zero deliveries under both algorithms. The highest delivery rates are on the shortest paths: TX--MI (3 hops) at $\sim$0.1 greedy / $\sim$1.0 MCF, and HOU--WAS (2 hops) at $\sim$0.37 greedy / $\sim$0.70 MCF. Delivered fidelities range from 0.82 to 0.90 across all pairs that receive any deliveries.
